---
title: "PhD Project - Experimental Study"
subtitle: "Design - First Trial &#x1F527;&#x1FA9A;&#x2699;"  
author: "Nicolas Bressoud"
date: "January 11, 2022"
team: "chEERS lab"
photo_creds: "[Med Badr Chemmaoui](hhttps://unsplash.com/photos/ZSPBhokqDMc)" 
url_unsplash: "https://images.unsplash.com/photo-1523726491678-bf852e717f6a?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1740&q=80"
background_position: "1050px 20px"
background_size: "100px"
output:
  xaringan::moon_reader:
    self_contained: false
    css: ["default", "xaringan-themer.css"]
    seal: false
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#D2202B",
  secondary_color = "#D2202B",
  inverse_header_color = "#FFFFFF",
  link_color = "#676C72",
    header_font_google = google_font("Josefin Sans")

)
```

class: title-slide, inverse, bottom
background-image: url(`r rmarkdown::metadata$url_unsplash`)
background-size: cover

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author` - `r rmarkdown::metadata$team`

### `r rmarkdown::metadata$date`

---
class: left middle

### Title
Strength-based approach at school and development of group cohesion : Perspectives on Inclusive Education

### Keywords
character strengths, group cohesion, inclusion

### Structure

1. Background
1. Objective et hypothesis
1. Method
1. Results (previsional)
1. Misc.
1. Timeline and next steps

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1469474968028-56623f02e42e?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2948&q=80")
background-size: cover

# Background

---
class: left middle

# Background

--

- Character Strengths 
- ...
- ...

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1581574919402-5b7d733224d6?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Goal and Hypothesis

---
class: left middle

# Goal and Hypothesis

--

- truc
- truc

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1555949963-ff9fe0c870eb?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Method

---
class: left middle

# Method - type of research

--

experimental design : Notre plan d’expérience est un plan intra et inter-individuel à mesures répétées 

---
class: left middle

# Method - participants

--

Participants
- nombre total
- âge, sex, type de scolarisation

---
class: left middle

# Method - Material

--

Material
- VI et measures
- VD et measures

---
class: left middle

# Method - Procedure

--

Procedure
- ethics : anonymisation, stockage des données, etc.
- experimental design
- quand comment

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1520004434532-668416a08753?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Results - Previsional

---
class: left middle

# Results - Previsional

--

quels resultats selon quelle analyse

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1623503664086-475867ec20b3?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=3173&q=80")
background-size: cover

# Miscellaneous

---
class: left middle

# Miscellaneous

--

financements
partenaires
conflicts of interest

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1518623001395-125242310d0c?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2880&q=80")
background-size: cover

# Timeline and next steps

---
class: left middle

# Timeline and next steps

--

truc

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1633613286848-e6f43bbafb8d?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Open questions

---
class: left middle

# Open questions

--

truc

---

class: middle

.left[


## &#x1F64F; Thank you!

]

--

.right[


Photo credits in order of appearance:

[Med Badr Chemmaoui](hhttps://unsplash.com/photos/ZSPBhokqDMc)

[David Marcu](https://unsplash.com/photos/78A265wPiO4)

[Engin Akyurt](https://unsplash.com/photos/bPiuY2ZSlvU)

[Shahadat Rahman](https://unsplash.com/photos/BfrQnKBulYQ)

[Kelly Sikkema](https://unsplash.com/photos/4JxV3Gs42Ks)

[Mats Hagwall](https://unsplash.com/photos/uzl47XdoLww)

[Vidar Nordli-Mathisen](https://unsplash.com/photos/Kuu5mmxkwW4)

[Towfiqu barbhuiya](https://unsplash.com/photos/oZuBNC-6E2s)

]
