---
title: "PhD Project - Experimental Study"
subtitle: "Design - First Trial &#x1F527;&#x1FA9A;&#x2699;"  
author: "Nicolas Bressoud"
date: "January 11, 2022"
team: "chEERS lab"
photo_creds: "[Med Badr Chemmaoui](hhttps://unsplash.com/photos/ZSPBhokqDMc)" 
url_unsplash: "https://images.unsplash.com/photo-1523726491678-bf852e717f6a?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1740&q=80"
background_position: "1050px 20px"
background_size: "100px"
output:
  xaringan::moon_reader:
    self_contained: false
    css: ["default", "xaringan-themer.css"]
    seal: false
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#D2202B",
  secondary_color = "#D2202B",
  inverse_header_color = "#FFFFFF",
  link_color = "#676C72",
    header_font_google = google_font("Josefin Sans")

)
```

class: title-slide, inverse, bottom
background-image: url(`r rmarkdown::metadata$url_unsplash`)
background-size: cover

# `r rmarkdown::metadata$title`

## `r rmarkdown::metadata$subtitle`

### `r rmarkdown::metadata$author` - `r rmarkdown::metadata$team`

### `r rmarkdown::metadata$date`

<p xmlns:cc="http://creativecommons.org/ns#" xmlns:dct="http://purl.org/dc/terms/"><a property="dct:title" rel="cc:attributionURL" href="https://bresnico.github.io/phd-11-janvier-2022/#1">PhD Meeting slides</a> by <a rel="cc:attributionURL dct:creator" property="cc:attributionName" href="https://nicolasbressoud.ch">Nicolas Bressoud</a> is licensed under <a href="http://creativecommons.org/licenses/by-nc/4.0/?ref=chooser-v1" target="_blank" rel="license noopener noreferrer" style="display:inline-block;">CC BY-NC 4.0<img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/cc.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/by.svg?ref=chooser-v1"><img style="height:22px!important;margin-left:3px;vertical-align:text-bottom;" src="https://mirrors.creativecommons.org/presskit/icons/nc.svg?ref=chooser-v1"></a></p>

---
class: left middle

### Title
Strength-based approach at school and development of group cohesion : Perspectives on Inclusive Education

### Keywords
character strengths, group cohesion, inclusion

### Structure

1. Background
1. Objective et hypothesis
1. Method
1. Results (previsional)
1. Misc.
1. Timeline and next steps

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1469474968028-56623f02e42e?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2948&q=80")
background-size: cover

# Background

---
class: left middle

# Background

--

### Topic

- Character Strengths (Peterson & Seligman, 2004)

- Importance of strengths use (identifying, developing, promoting) (Linkins et al., 2015)

--

### Impact

- Benefits for relationships in the classroom (Quinlan et al., 2014)

--

- **Potential impact on inclusive settings (positive emotions, affiliation need, prosocial behavior)**

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1581574919402-5b7d733224d6?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Goal and Hypothesis

---
class: left middle

# Goal and Hypothesis

--

### Two main questions

- How can we support strengths knowledge and use?

- Does it have an impact on the classroom climate?

--

### Hypothesis

- The use of strengths at school can be improved with a program of 10 30-minute sessions. 

- Strengths use predicts class cohesion (**positive emotions**, **need of affiliation**, **prosocial behavior**).

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1555949963-ff9fe0c870eb?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Method

---
class: left middle

# Method

--

- Type of research
- Participants
- Material
- Procedure

---
class: left middle

# Method - Type of research

--

Quasi-experimental design:

--

- Repeated measures (before, after)

- Between and within subjects

- No random assignation

---
class: left middle

# Method - Participants

--

- Population: Pupils

- Age: 8 to 10 years old

- Type of schooling: ordinary/integrative settings

- N: 120 to 160, 8 classes (4 in each condition group)


---
class: left middle

# Method - Material

--

### IV - Strengths use (better than strengths knowledge)

- Measured with the Strength Use Scale (Govindji & Linley, 2007)

- Has to be adapted (and validated) in french, for children

- 14 items, self reported

--

### DV - Positive emotions, need of affiliation, prosocial behavior

- Positive emotions: PANAS ?

- Need of affiliation: ...

- Prosocial Behavior: ... 

- *Completed with a sociogramm (qualitative observation of relational dynamics)*

---
class: left middle

# Method - Procedure

--

### Ethics

- with UniDistance

- Anonymization, Data storage, Consent, Approvals,...

--

### Design

- Experimental group:

    - Use of the strengths material by the teacher (10 x 30 min)
    - 2 sessions per week over 5 weeks
    - Coaching by the experimenter (1 time before and 2 times during the procedure)

- Measures before and after intervention in both experimental and control groups

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1520004434532-668416a08753?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Results - Previsional

---
class: left middle

# Results - Previsional

--

Standard paired t-test might indicate:

- Progression of the experimental group in strengths use

--

Multilevel analysis might indicate:

- Effect of interaction time-group on DV
    
    - Positive emotions
    - Need of Affiliation
    - Prosocial behavior

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1623503664086-475867ec20b3?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=3173&q=80")
background-size: cover

# Miscellaneous

---
class: left middle

# Miscellaneous

--

- Funding: none

- Collaborations:

    - HEP Valais
    - UniDistance
    - UNIFR
    - HEP Vaud
    - Université Lyon Lumière
    
- Conflicts of interest: none

---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1518623001395-125242310d0c?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2880&q=80")
background-size: cover

# Timeline and next steps

---
class: left middle

# Timeline and next steps

--

### January-February: ethical approval
### March-June: Data collect

- week 1: T1
- week 2 to 7: Intervention
- week 8: T2
---
class: title-slide, inverse, middle
background-image: url("https://images.unsplash.com/photo-1633613286848-e6f43bbafb8d?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=2940&q=80")
background-size: cover

# Open questions

---
class: left middle

# Open questions

---

class: middle

.left[


## &#x1F64F; Thank you!

]

--

.right[


Photo credits in order of appearance:

[Med Badr Chemmaoui](hhttps://unsplash.com/photos/ZSPBhokqDMc)

[David Marcu](https://unsplash.com/photos/78A265wPiO4)

[Engin Akyurt](https://unsplash.com/photos/bPiuY2ZSlvU)

[Shahadat Rahman](https://unsplash.com/photos/BfrQnKBulYQ)

[Kelly Sikkema](https://unsplash.com/photos/4JxV3Gs42Ks)

[Mats Hagwall](https://unsplash.com/photos/uzl47XdoLww)

[Vidar Nordli-Mathisen](https://unsplash.com/photos/Kuu5mmxkwW4)

[Towfiqu barbhuiya](https://unsplash.com/photos/oZuBNC-6E2s)

]
